Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2022-01-27 Manuscript/FLPhish(Trans).tex
introduction修改完毕

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Bonawitz \textit{et al.} in Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data from each user, the central server in FL only needs to aggregate its global model using model updates from distributed clients. In each iteration of FL, the central server sends a model to each client. The client uses its private data to update the model and sends the model gradient update back to the central server. Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model. Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.

\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system. On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. On the other hand, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}. And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches aim to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregation process. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another type of Byzantine-robust approach (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and selects the median value of each parameter as the value to be used in global model updates. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) to defend against Byzantine attacks in Ensemble FL. Our contributions are four-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose an aggregation rule, called FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}

>>>>

\section{Introduction}
\IEEEPARstart{M}{any} elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are acquired by the application developers from users, such as the shopping app users' purchase record data, patients' clinical data and etc. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from users anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Bonawitz \textit{et al.} built the first FL system which is operated on Google's mobile phone to train a global model based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. Furthermore, some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

\par FL is a distributed machine learning paradigm, which allows the central server in the paradigm to produce a global model without getting each individual's private data. Instead of gathering private data from each user, the central server in FL aggregates all the model gradient updates from distributed clients to its global model. In each iteration of FL, the central server sends a model to each client. Each client updates the model using its private data and sends the model gradient update back to the central server. In the central server, all the clients' updates are aggregated to a global model gradient update, and the global model gradient update is utilized to update the global model. Thus, FL not only protects each participating individual's privacy, but also leverages the capabilities of the end users' computation and storage.

\par Since thousands of clients from different sources may participate in the training process, security issues also exist in the distributed FL system. On one hand, former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. On the other hand, FL faces threats from the poisoning attacks launched by malicious attackers among the FL clients \cite{miao2018attack, laishram2016curie}. And such attacks are referred to as Byzantine attacks in wireless communication network \cite{ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the global model to learn incorrect knowledge. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be separated into two types according to the attack consequences: targeted attacks and untargeted attacks. In untargeted attack, the disturbed global model make wrong predictions for all the samples in the test dataset \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In targeted attacks, wrong predictions are produced by the global model only for the chosen samples in the test dataset \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malicious Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. Byzantine-robust techniques try to construct a global model with high accuracy in the presence of a finite number of malicious clients. According to their different mechanisms, we divide Byzantine-robust approaches into two major types. The first (named Byzantine-Detection) is based on the development of a Byzantine-robust aggregation algorithm that distinguishes suspected clients from benign clients. The suspected clients' gradient updates are subsequently removed from the aggregation process by the server. For instance, in the DRACO scheme proposed by Chen \textit{et al.}, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another Byzantine-robust technique (named Byzantine-Tolerance) seeks to ensure that the aggregation process is tolerant to poisoned updates from Byzantine clients without excluding Byzantine clients like Median \cite{ref_16_defense}. In Median, The FL server sorts the values of each parameter and picks the median value of each parameter as the value to be utilized in global model updates. In this study, we provide an unique reputation-based phishing method (named FLPhish) to protect against Byzantine attacks in Ensemble FL, based on the preceding research. Our contributions are four-fold:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by for it is compatible with different deep learning models in different clients.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients with higher accuracy.
  \item We propose an aggregation rule, called FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate in the aggregation process.
\end{itemize}
